---
title: "MATH 4650 - Project 2"
author: "Alexander Kahanek"
date: "4/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
```

```{r}
raw <- read.csv('1970lottery.csv')

raw %>% head()
```

## question 1 -- scatterplot

```{r}
raw %>% 
  ggplot(aes(x = Day_of_year, y = Draft_No)) +
  geom_point() + 
  labs(title = "A comparison of the day of the years and its respective draft number")
```

## part of Q1 (not actually needed)


```{r}
raw %>% 
  select(Draft_No, Day_of_year) %>% 
  cor()
```

## Question 2 -- simple linear regression model

```{r}
model <- lm(Draft_No ~ Day_of_year, data = raw)
```

## Question 2 -- QQ plot

```{r}
model %>% 
  plot()
```

## Question 3 -- change linear model?

Tried sqrt and log on independant and dependant variables, each attempt had no beneficial effect.

```{r}
linear <- lm(sqrt(Draft_No) ~ sqrt(Day_of_year),data = raw)

linear %>% 
  summary()
```


```{r}
linear %>% 
  plot()
```

## Question 4 -- boxplots

```{r}
raw %>% 
  ggplot() +
  geom_boxplot(aes(x = as.factor(Month_Number), y = Draft_No)) +
  scale_x_discrete(labels = c("Jan", "Feb", "Mar", "Apr", "May", "June", "July", "Aug", "Sep", "Oct", "Nov", "Dec")) + 
  labs(title = "A comparison of the distributions of draft number across the months")
```

## Question 5 -- anova across months

```{r}
aov(Draft_No ~ Month, data = raw) %>% summary()
```

## Question 5 -- testing parametric and homgeneity of variance

```{r}
raw %>% 
  group_by(Month) %>% 
  summarise(
    month_number = max(Month_Number)
    ,length = n()
    ,variance = var(Draft_No)) %>% 
  arrange(month_number)
```

## Question 5 -- other tests

```{r}
kruskal.test(Draft_No ~ Month, data = raw)
```


```{r}
library(FSA)
dunnTest(Draft_No ~ Month, data = raw, method = 'bh')
```
