---
title: "INFO 3010 - Assignment 3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spring 2020 by Lingzi Hong
## Due: Monday, Feb 10, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Fill in the code chunks and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 
Special thanks to: https://archive.ics.uci.edu/ml/datasets/bank+marketing for sharing the dataset.

### Input variables:
####Bank Client Data:
1 - age (numeric)

2 - job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')

3 - marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)

4 - education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')

5 - default: has credit in default? (categorical: 'no','yes','unknown')

6 - housing: has housing loan? (categorical: 'no','yes','unknown')

7 - loan: has personal loan? (categorical: 'no','yes','unknown')

####Related with the last contact of the current campaign:
8 - contact: contact communication type (categorical: 'cellular','telephone') 

9 - month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')

10 - day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')

11 - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.
Other Attributes:

12 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)

13 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)

14 - previous: number of contacts performed before this campaign and for this client (numeric)

15 - poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')
Social and Economic context attributes

16 - emp.var.rate: employment variation rate - quarterly indicator (numeric)

17 - cons.price.idx: consumer price index - monthly indicator (numeric) 

18 - cons.conf.idx: consumer confidence index - monthly indicator (numeric) 

19 - euribor3m: euribor 3 month rate - daily indicator (numeric)

20 - nr.employed: number of employees - quarterly indicator (numeric)

####Output variable (desired target):
21 - y - has the client subscribed a term deposit? (binary: 'yes','no')



### Q1. (5pts) Import the dataset 'bank.csv' and assign it to a variable called df.
```{r}
df <- read.csv("bank.csv")
```

### Q2. (5pts) See the first 10 lines.
```{r}
head(df,10)
```

### Q3. (5pts) What is the number of observations in the dataset?
```{r}
nrow(df)
```

### Q4. (5pts) Print the name of all the columns.
```{r}
colnames(df)
```

### Q5. (5pts) How many people have 'cellular' as contact type?
```{r}
nrow(df[df[,'contact']=='cellular',])
```

### Q6. (5pts) What is the marital status of people who completed only 'Primary' education?
```{r}
df[df[,'education']=='primary','marital']
```

### Q7. (5pts) What is the average age of the people?
```{r}
mean(df[,'age'])
```

### Q8. (5pts) What is the average balance for all the people who are retired?
```{r}
mean(df[df[,'job']=='retired','balance'])
```

### Q9. (5pts) Which job has the most balance?
```{r}
max_bal <- max(df[,'balance'])
max_person <- df[df[,'balance']== max_bal,]
print(max_person[,'job'])
```

### Q10. (5pts) How many people who completed tertiary education are married?
```{r}
nrow(df[df[,'education']=='tertiary' & df[,'marital']=='married',])
```

