---
title: "INFO 3010 - Assignment 8"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spring 2020 by Lingzi Hong
## Due: Monday, April 13, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Please download the snowstorm.json from canvas. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 

```{r}
library(dplyr)
library(ggplot2)
library(GGally)

#making life ezpz
tt_split <- function(data, percent, side){
  ## FUNCTION FOR SPLITTING BY PERCENT CHOSEN
  if(side == 'top'){
    data <- data %>% #top X% of data
      slice(1:ceiling(nrow(data)*percent))
  }
  else if (side == 'bot'){
    data <- data %>% #bottom X% of data
      slice(ceiling(nrow(data)*percent)+1:nrow(data))
  }
  else{
    print("choose top or bot portion of data")
  }
  return(data)
}
```

### Q1. (5pts)  Create a function that can convert fahrenheit to celsius. The formula is (F-32)*5/9 = C. Fill in the function body. There is a test case to convert fahrenheit 86 to celsius. 
```{r}
convert_F2C <- function(num){
  num = (num-32)*5/9
  return(num)
}

convert_F2C(86)
```

### Q2. (5pts) Read the file '2016.csv' to a dataframe. Check the first 5 lines of the data. 
```{r}
df <- read.csv('2016.csv')
df %>% 
  head(5)
```

### Q3. (5pts) Use the dataframe in Q3. Compute the average Hapiness_Score for countries in North America. 
```{r}
df %>% 
  subset(Region == "North America") %>% 
  summarise(
    Region = "North America",
    mean_hap = mean(Happiness_Score)
  )
```

### Q4. (5pts) Use the dataframe in Q3. Write code to compute the difference in Generosity between United States and Mexico.
```{r}
us_gen <- df %>%
  subset(Country == "United States", select = Generosity) %>%
  as.numeric()

mex_gen <- df %>%
  subset(Country == "Mexico", select = Generosity) %>%
  as.numeric()

us_gen - mex_gen
```

### Q5. (5pts) Use the dataframe in Q3. Plot the dataframe columns Happiness_Rank and Happiness_Score as a line graph

```{r}
df %>% 
  ggplot(aes(x=Happiness_Rank, y=Happiness_Score)) +
  geom_line()
```

### Q6. (5pts) Use the dataframe in Q3. Plot the scatter plot matrix for the four variables: Family, Life_Expectancy,Freedom, Generosity
```{r}
df %>%  
  subset(select = c(Family, Life_Expectancy, Freedom, Generosity)) %>%
  ggpairs()
```

### Q7. (5pts) Get a subset of data with countries from Region of "Western Europe" and "North America" and "Eastern Asia".
```{r}
regions = c("North America", "Western Europe", "Eastern Asia")

reg_data <- df %>% 
  subset(Region %in% regions)
```
### Q8. (5pts) Use the subset data in Q8. Draw a scatter plot with Government_Corruption in the x-axis, Freedom in the y-axis, and the points are colored by region. 
```{r}
reg_data %>% 
  ggplot()+
  geom_point(aes(x=Government_Corruption, y= Freedom, color = Region))
```

### Q9. (5pts) Build a linear regression model: predict Happiness_Score with variables GDP_per_Capita, Family, Life_Expectancy and Freedom. 
```{r}
data <- df %>% 
  subset(select = c(Happiness_Score, GDP_per_Capita, Family, Life_Expectancy, Freedom))

train <- data %>% 
  tt_split(0.8, 'top')

test <- data %>% 
  tt_split(0.8, 'bot')

lm.fit <- lm(Happiness_Score ~ GDP_per_Capita + Family + Life_Expectancy + Freedom,
               data = train)
```

### Q10. (5pts) Get a summary of the model. Answer the following questions out of the code chunk: what is the adjusted R-squared? What is the coefficient of GDP_per_Capita?
```{r}
lm.fit %>% 
  summary()
```

When Happiness Score is 0, we can expect the values of our Predictors to be 2.4807.

The estimated coefficient in GDP per Capita is 0.7099, this tells us that when the Happiness score increases by 1 point, we should expect the GDP score to increase by 0.7099

Std. Error is an estimate of variability, t value = est/std error, how big is the error, relative to my estimates. The P value tells us how statistically significant our factors are. When p is significantly small, we can reject the null hypothesis and claim that the factor is statistically significant.

Residual standard error is the Root Mean Square Error, which is 0.5115 for this model. This tells us that, on average, the model has an error of ~0.5 when predicting the Happiness Score

The Multiple R-squared value is 0.6963, this means that about 70% of the Happiness Score can be explained by the variations in the other four factors.

The Adjusted R-squared becomes lower when variables are added to the model that have no relation to the predictions. Both our R-squared values are very close to eachother, this would suggest that all of the factors are statistically significant to predict the Happiness Score.

The F statistic shows how well the model does compared to the error. Measuring the significance of the overall model. The higher the F value, tells us that the model explains more than the actual data itself. It also tells us the degree of freedoms of the model aswell as the data. As we have 4 predictors, the df for the model is 4.

The final p-value is very close to zero, suggesting that the overall model is statistically significant.