---
title: "INFO 3010 - Assignment 7"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spring 2020 by Lingzi Hong
## Due: Monday, April 6, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Please download the snowstorm.json from canvas. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1. (5pts) Read the file "2015.csv" to a dataframe. Have a statistical summary of the dataset. 
```{r}
options(stringsAsFactors=FALSE)
library(plyr)
library(dplyr)
library(ggplot2)
df <- read.csv("2015.csv")
df %>% 
  summary()
```

### Q2. (5pts) Draw a plot with box plot of Happiness_Score for countries in each Region group.
```{r}
df %>% 
  ggplot(aes(Region, Happiness_Score, color = Region)) + geom_boxplot(stat="boxplot")
```

### Q3. (10pts) Draw a scatter plot matrix for variables: Happiness_Score, Family, Life_Expectancy and Generosity
```{r}
df %>% 
  subset(select = c(Happiness_Score, Family, Life_Expectancy, Generosity)) %>% 
  pairs()
```

### Q4. (10pts) Build a linear regression model to predict Life_Expectancy with Hapiness_Score, GDP_per_Capita, Family and Government_Corruption. 
```{r}
LE_model <- lm(Life_Expectancy ~ Happiness_Score + GDP_per_Capita + Family + Government_Corruption, data = df)
```

### Q6. (10pts) Check model details. Answer the following questions out of code box: What is the adjusted R-squared value? Is the linear relation significant? 

```{r}
LE_model %>% 
  summary()
```

The adjustted r squared value is 0.3901. Since the values for the for Happiness_Score and Government_Corruption are very close to 0, the null hypothesis is rejected, stating that there is a statistically significant relationship between Life Expectancy and Happiness Score, as well as Life Expectancy and Government Corruption. 


### Q7. (10pts) Draw diagnostic plots for the model in Q6. 
```{r}
LE_model %>% 
  plot()
```

