---
title: "INFO 3010 - Assignment 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## by Lingzi Hong
## Due: Monday, Jan 27, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Submit this downloaded completed R markdown file in the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1: Compute the following values. Write code in the below chunks.

(a) 27(38-17)  (3pts)
```{r}
x=27*(38-17)
print(x)
```

(b) log(3^4)  (4pts)
```{r}
log(3^4)
```

(c) square root of 217 (4pts)
```{r}
x=sqrt(217)
print(x)
```

### Q2: Create the following vectors. a = (5, 10, 15, 20, 70, 160), b = (87, 86, 85, 33, 58, 56). 

(a) create a vector c, which is add results of vector a and b (3pts)
```{r}
a=c(5,10,15,20,70,160)
b=c(87,86,85,33,58,56)
n=1
while (n<=6) {
  x[n]<-a[n]+b[n]
  n=n+1
}
print(x)
```

(b) get the 2st and 5th element of c  (4pts)
```{r}
print(x[2])
print(x[5])
```

(c) how many elements of c are greater than 50 (4pts)
```{r}
n<-1
count<-0
while (n<=length(x)){
  if (x[n]>50){
    count <- count +1
  }
  n = n+1
}
cat("There are",count,"elements greater than 50.")

```

### Q3: Use c from problem 2, compute the following statistics of c:
(a) sum (3pts)
```{r}
print(sum(x))
```

(b) median (4pts)
```{r}
print(median(x))
```

(c) summary statistics of c (4pts) 
```{r}
summary(x)
```

### Q4: Create the following vectors with seq or rep
(a) c(1,3,5,7,9)  (3pts)
```{r}
vect1=seq(1,9,by=2)
print(vect1)
```

(b) c(1,2,3,4,1,2,3,4) (4pts)
```{r}
vect2=rep(1:4,times=2)
print(vect2)
```

(c) c(10,8,6,4,2) (4pts)
```{r}
vect3=seq(10,2,by=-2)
print(vect3)
```

### Q5: create a numeric vector (0,1,0,0,1,1), change it to a vector of characters ("0","1","0","0","1","1"). (4pts)
```{r}
num_vect=c(0,1,0,0,1,1)
char_vect = as.character(num_vect)
print(char_vect)
```

### Q6: write a function, for every element in a vector, if the data type if character, print 'error'. Finally return number of characters in the vector. (6pts)
```{r}
vect3<-c("a","b","c")
Count_Chars <- function(x) {
  n=1
  count=0
  while (n <= length(x)) {
    if (is.character(x[n])==1){
      count <- count+1
      print("error")
    }
    n=n+1
  }
  return(count)
}
cat("There are",Count_Chars(vect3),"characters in that vector.")
```
