---
title: "INFO 3010 - Assignment 6"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spring 2020 by Lingzi Hong
## Due: Monday, Mar 23, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Please download the snowstorm.json from canvas. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 
4. You can get 5 bonus points for using ggplot2 package.


### Q1. (5pts) Download the 'HousePrice.csv' dataset. Read the dataset to a dataframe. Check the structure of the dataframe.
```{r}
library(ggplot2)
df <- read.csv("HousePrice.csv")
head(df)
```

### Q2. (5pts) Draw a histogram to check the distribution of house price.
```{r}
ggplot(df) +
  geom_histogram(aes(Price))

#the plot is Positively skewed, with a right sided long tail
```

### Q3. (5pts) Draw a density plot to check the distribution of Sqft_Area of houses. 
```{r}
ggplot(df)+
  geom_density(aes(Sqft_Area))

#looks very similar to our bar graph
```

### Q4. 1) (5pts) Get a subset of data with postal code as "98178","98146" and "98118".  2) (10pts) Draw a scatter plot with the subset data. It has Sqft_Area in x-axis, Price in y-axis. The dots are colored by postal code.  
```{r}
df_zip <- df[df[,"Postal"]== c(98178,98146, 98118),]

ggplot(df_zip)+
  geom_point(aes(x=Sqft_Area, y=Price, color = Postal))

#not sure why it is giving a warning here
```


### Q6. (10pts) Randomly choose a dataset you are interested. You may also keep using the hourseprice dataset. Draw a scatter plot matrix. What do you find? Write 2-3 sentences about your finding. Remember to write the sentences outside of code chunk.

```{r}
df_bed <- df[df[,"Bed"]== c(5,4,3,2,1),]

ggplot(df_bed, aes(Price, Price_Sqft, color = Bed))+
  geom_point(shape = 1)+
  geom_smooth(method = lm, color = "black")+
  facet_wrap(~Bed)

#Here we can see that for 1 and 5 bedroom houses, there seems to be a stronger correlation between their total price, and their price per sqft. However, for 2, 3, and 4 bedrooms we see a lower correlation between price and price per square foot. However, we also have fewer datapoints for the 1 and 5 categories, which could be an explaination.
```

### Q7. (10pts) Draw a line plot with the chosen dataset. What do you find? Write 2-3 sentences about your finding.
```{r}
df_crime <- df[,c("Sqft_Area", "Built_Year")]

ggplot(df_crime, aes(Built_Year, Sqft_Area))+
  geom_line()+
  geom_smooth()

#Here we can see that the average sqft has stayed roughly the same throughout the build years. There is a small dip, followed by a quick rise, in 1950 however. Our regression line seems to be trending upwards.
```
